Delivering reliable software in the European scientific arena: evolution of methodologies and new trend analysis

### 2017-11-30 paper-ieee-trans.tex
add text and new image for devops for applications

@@

Two pilot infrastructures are at the disposal of developers and scientific
communities involved in the project. The aim of these testbeds is to test the
level of integration between the components involved in the INDIGO--DataCloud
solution and use cases validation, by deploying and executing the applications
with the last stable version of the software.

@@

>>>>

\subsection{DevOps adoption from user communities}

The experience gathered throughout the project with regard to the adoption of
different DevOps practices is not only useful and suitable for the software related
to the core services in the INDIGO-DataCloud solution, but also applicable to the
development and distribution of the applications coming from the user communities.

Two applications from WP2, DisVis \cite{disvis} and PowerFit \cite{powerfit}, were
integrated into a similar CI/CD pipeline described in section \ref{sec:devops}.
Figure \ref{fig:fig_disvis} shows the pipeline for the Disvis application.

User application developers were provided with both a means to validate the
source code before merging and the creation of a new versioned Docker image,
automatically available in the INDIGO-DataCloud’s application repository.

The novelty introduced in the pipeline above is the validation of the application.
Once the application is deployed as a Docker container, and subsequently uploaded
to the Dockerhub repository, it is instantiated in a new container to be validated.
The application is then executed and the results compared with a set of reference outputs.
Thus this pipeline implementation goes a step forward by testing the application
execution for the last available Docker image in the catalogue.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{images/disvis.png}
\caption{DevOps pipeline to distribute Docker images for Disvis application.}
\label{fig:fig_disvis}
\end{figure*}

@@

Two pilot infrastructures are at the disposal of developers and scientific
communities involved in the project. The aim of these testbeds is to test the
level of integration between the components involved in the INDIGO--DataCloud
solution and use cases validation, by deploying and executing the applications
with the last stable version of the software. A map of the Pilot Preview
infrastructure is depicted in Fig. \ref{fig:fig_pilotpreview}, it shows the
resources providers and the components or services they deployed and supported.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{images/pilotpreview.png}
\caption{Resource centers supporting the Pilot Preview testbed and corresponding
set of deployed INDIGO-DataCloud components or services.}
\label{fig:fig_confman}
\end{figure*}

@@

\bibitem{disvis} G.C.P. Van Zundert, A.M.J.J. Bonvin,
DisVis: quantifying and visualizing the accessible interaction space of distance
restrained biomolecular complexes, Bioinformatics 31 (2015) 3222–3224

\bibitem{powerfit} G.C.P. Van Zundert, A.M.J.J. Bonvin,
Fast and sensitive rigid-body fitting into cryo-EM density maps with PowerFit,
AIMS Biophys. 2 (2015) 73–87.
